|

### 2021-03-01 manuscript/article.Rmd
add intro

---
title:  |
        | **Deaths and Disappearances in the Pinochet Regime: A New Dataset**
author: 
  - "Danilo Freire[^df]"
  - "John Meadowcroft[^jm]"
  - "David Skarbek[^ds]"
  - "Eugenia Guerrero[^eg]"
date: \today
thanks: "We thank Umberto Mignozzetti and Robert Myles McDonnell for their helpful comments. Data and replication information are available at [`http://github.com/danilofreire/pinochet-dataset`](http://github.com/danilofreire/pinochet-dataset)."
abstract: "... However, . This paper presents a georeferenced event dataset on "
keywords: "authoritarian regimes, Chile, geocoded event data, Pinochet, truth commission"
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    template: template.latex
---

# Introduction\label{sec:intro}

\setlength{\parindent}{1cm}
\setlength{\parskip}{0pt}

# Conclusion: New Avenues for Research

In this paper, we discuss a quantitative presentation of the Report of the Chilean National Commission on Truth and Reconciliation [-@report1991], which described more than two thousand human rights abuses perpetrated by the Pinochet regime from 1973 to 1990.

The dataset includes rich information about more than 2,0000 victims of the Pinochet regime, the geographical location of the incidents, and the specific date when the violations occurred. The graphs and maps shown in this article provide some preliminary results about the temporal and spatial variation of state-sponsored violence during the recent military period in Chile.

We believe our data opens a number of potential research avenues. First, scholars can use the dataset to evaluate the long-term impacts of human rights violations on several outcomes of interest. For example, XXX and XXX highlight that state-led violence has enduring effects on social polarisation, political outcomes, and economic development. Researchers can test whether the Pinochet regime caused a similar impact on Chile's economy and society. Moreover, sociologists and criminologists may be interested in the relationship between the intensity of the human rights abuse and post-regime levels of social unrest or interpersonal violence.

Second, the dataset enables researchers to analyse the inner dynamics of authoritarian governments. This topic remains understudied in political science due to a lack of disaggregated information. By linking human right abuses to changes in Pinochet's support coalition, scholars can explore whether the violations affected levels of civilian or bureaucratic collaboration to the regime. XXXXXXXXXXXXX.

Finally, scholars can investigate the connections between international legitimacy and domestic politics in repressive regimes. This is a promising area of research as the Chilean government and American intelligence services continue to declassify documents from the Pinochet era. One relevant question is whether pressure from foreign governments and organisations had any influence over the levels of human rights abuses in Chile. We hope our dataset is useful for scholars interested in these and other questions, and that the information it contains elicits hypotheses not only about the Pinochet period, but about authoritarian governments more generally.

[^df]: Postdoctoral Research Fellow, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, [`danilofreire@gmail.com`](mailto:danilofreire@gmail.com), [`http://danilofreire.github.io`](http://danilofreire.github.io). Corresponding author.

[^jm]: Senior Lecturer in Public Policy, Department of Political Economy, King's College London, [`john.meadowcroft@kcl.ac.uk`](mailto:john.meadowcroft@kcl.ac.uk), [`http://johnmeadowcroft.net`](http://johnmeadowcroft.net).

[^ds]: Associate Professor, Department of Political Science and the Political Theory Project, Brown University, [`david_skarbek@brown.edu`](david_skarbek@brown.edu), [`http://davidskarbek.com`](http://davidskarbek.com).

[^eg]: Software Developer, Tempo UK.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{6pt}

>>>>

---
title:  |
        | Human Rights Violations in the Pinochet Regime:
        | A Quantitative Presentation of the Rettig and Valech Reports
author: 
  - Mauricio Carrasco[^auth01]
  - Danilo Freire[^auth02]
  - Pablo Seguel Gutierrez[^auth03]
date: \today
thanks: "The authors thank Eugenia Guerrero, John Meadowcroft, and David Skarbek for their work on the Rettig Report dataset. All replication materials and the source code for the `pinochet R` package are available at <https://github.com/danilofreire/pinochet>."
abstract: "This article introduces a new dataset on human rights violations during the Pinochet regime in Chile (1973-1990). Based on previous work by @freire2019dataset, we code all cases of deaths and disappearances recorded in the Rettig (1991), Valech I (2004), and Valech II (2005) reports. Our dataset includes XX variables and presents information on XXXX individuals, of which XXX appear in at least two reports. We also provide geographical coordinates for all locations of human rights abused mentioned in the three reports. The data are available in several formats, including an `R` package built especifically for our purposes. The paper shows the temporal and spatial variation of human rights violations during the regime, and proposes further avenues of research for those interested in Chilean history and cross-national studies of state-sponsored violence."
abstractspacing: double
keywords: Chile; human rights violations; Pinochet; state-sponsored violence; truth commission
jelcodes: 
fontsize: 12pt
margin: 2cm
urlcolor: darkblue
linkcolor: Mahogany
citecolor: Mahogany
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

```{r setup, message=FALSE, warning=FALSE, echo=FALSE}
# If you need to install any package while knitting the document
r <- getOption("repos")
r["CRAN"] <- "https://cran.rstudio.com/"
options(repos = r)

# Chunk definitions
def_chunk_hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def_chunk_hook(x, options)
  ifelse(options$size != "normalsize",
         paste0("\n \\", options$size, "\n\n", x,
                "\n\n \\normalsize"), x)
})

# Install packages
packages <- c("kableExtra", "scales", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

# Read dataset
library(readr)
df <- read_csv("../data/victims.csv")
```

[^auth01]: Author information. 
[^auth02]: Independent Researcher,
[`danilofreire@gmail.com`](mailto:danilofreire@gmail.com),
<https://danilofreire.github.io>.
[^auth03]: Author information.

\newpage

# Introduction
\label{sec:intro}

General Augusto Pinochet ruled Chile with an iron fist from 1973 to 1990. Later
findings show that the Chilean Armed Forces and the government's secret police
carried out gross human rights violations against political dissidents,
including murders, beatings, waterboarding, and kidnappings [@ensalaco2000chile;
@huneeus2007pinochet; @verdugo2001chile]. Most of the repression occurred in the
first months of the military regime, but state terrorism continued until the
last years of the dictatorship, often in collaboration with other Latin American
countries [@dinges2005condor; @mcsherry2012predatory]. While the true extension
of the brutality of the Pinochet regime remains unknown, estimates suggests that
the number of victims may be close to 30,000 [@weissbrodt1992report].

In this paper, we provide a quantitative presentation of all cases of deaths and
disappearances recorded in the Rettig and Valech reports. Both reports were
elaborated at the request of the Chilean government and are the official sources
of information on serious human rights abuses during the Pinochet years. The
National Commission for Truth and Reconciliation Report, also known as the
Rettig Report after its main editor Raúl Rettig, was compiled in 1991 and
recorded more than 2,000 cases of murder and kidnappings from 1973 to 1990
[@rettig1991report]. In 2004, a commission chaired by Bishop Sergio Valech
produced another compilation of victims of the military dictatorship, which
complemented and expanded the original findings [@valech2004report]. The Valech
report was updated in 2010 to include more cases.

Our dataset contains `r ncol(df)` variables and `r comma(nrow(df))`
observations. The data describes personal characteristics of the victims -- such
as unique id, name, age, gender, and occupation -- as well as information about
the crimes, including the type, perpetrator, and geolocation whenever such
information was available in the reports. We formatted the dataset following the
principles of "tidy data", in which each row correspondents to one case, each
variable forms a column, and the data are represented as a table
[@wickham2014tidy]. Moreover, we provide three different presentations of the
data. The first table includes only the cases mentioned in Rettig Report, the
second is the data from the Valech Report, and in the final table we merged all
cases together. To make the data easily available to users, we provide a
companion `R` package, named `pinochet` [@freire2019pinochet], alongside `csv`
and `xlsx` files that scholars can download at
<http://github.com/danilofreire/pinochet>.

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}
